Temporal Development of Overlapping Communities in Co-Authorship Networks

### 2015-12-02 paper/typeinst.tex
some text to evolution

\section{Clique Percolation Method}
Clique percolation method (CPM) is used to identify overlapping communities in networks. The following section summarizes the main findings regarding co-authorship networks and the algorithm used in the paper \emph{Uncovering the overlapping community structure of complex networks in nature and society} by Palla, Derenyi, Farkas and Vicsek.

@@

\subsection{Algorithm}
Based on the explained community definition the algorithm consists of the following steps, which will be explained in more detail. [TODO an example of a graph in each step of the algorithm can be seen in figure X].

@@

\subsection{Details on $k$ \& $w^*$ for co-authorship networks}
calculation of link weights $1/(n-1)$, with $n$ number of authors per paper. Treshold $w^*$ for link weights. This is how collaboration is weighted or defined.

@@

\section{Community Evolution based in CPM}
TODO

>>>>

\section{Clique Percolation Method}
\label{cpm}
Clique percolation method (CPM) is used to identify overlapping communities in networks. The following section summarizes the main findings regarding co-authorship networks and the algorithm used in the paper \emph{Uncovering the overlapping community structure of complex networks in nature and society} by Palla, Derenyi, Farkas and Vicsek.

@@

\subsection{Construction of the co-authorship network}
TODO, how are weights calculated in this network, what is a collaboration here.

\subsection{Algorithm}
Based on the explained community definition the algorithm consists of the following steps, which will be explained in more detail. [TODO an example of a graph in each step of the algorithm can be seen in figure X]. The starting point for the algorithm is a undirected unweighted graph. In section \ref{cpm-construction} we talk about generating an unweighted collaboration, co-authorship graph.

@@

\subsection{Construction of the network and Details on $k$ \& $w^*$ for co-authorship networks}
\label{cpm-construction}
also talk about choosing the right k and the rigth trashhold. Calculation of link weights $1/(n-1)$, with $n$ number of authors per paper. Treshold $w^*$ for link weights. This is how collaboration is weighted or defined.

@@

\section{Community Evolution based in CPM}
\label{evolution}
Palla et.~al developed \cite{palla2007quantifying} in 2007 an algorithm based on clique percolation that allows us to investigate the time dependance of overlapping communities on a large scale, thus uncovering basic relationships characterizing community evolution.
sumary

\subsection{Construction of the time dependant networks}
Event in the network are paper publications. Social connection between people start before event and lastet for some time after the event, the higher the fequency the closer the relationship[TODO citeSocial intertia in collaboration networks, Ramosco and Morris 2006]

Weight is $n/(n-1)$ for each paper and its collaborators.
The \emph{link weight} between to nodes $a$ and $b$ at a certain time $t$ is calculated as

$$w_{a,b}(t)= \sum_{i}^{} w_i e^{\frac{-\lambda \left|t-t_i\right|}{w_i}}$$

The summation runs over all collaboration event in which $a$ and $b$ are involved. The event $i$ occurs at time $t_i$ and the corresponding edge weight at this time is called $w_i$. This function which looks like a decay functions kind of models the strenght of collaboration between authors over time considering all event ever occured in time.

A treshhold $w^*$ is used to only include certain edges to the time dependant graph. So for each timestep a graph can be constructed based on the collaboration strenght in each time step.

here in the co-authorship network $k=3, w^*=1.0$ is used.

what are the time steps for co-author network [TODO find out read again]

\subsection{Algorithm}
The algorithm uses the clique percolation method to find communities in each time depandent graph. The starting point is set of an undirected and unweighted  graphs for each timestep (snapshots usually called in other papers)

\begin{enumerate}
\item[(1)] Extract communities with CPM for each time step.
\item[(2)] Match the set of communities at succeeding time steps (far from trivial). 
\end{enumerate}

As (1) was already explained in section~\ref{cpm} we focus on (2) the matching of set of communities between consecutive time steps [is it really consecutive or only after one another?]

\subsection{Summary of variables an measured statistics}
the overall coverage of the community structure (ratio of nodes contained in at least one community) is measured\\
distribution of community size is measured too\\

\subsection{Main Findings of the paper}
difference between big and small communities and development over time
